Specific leaf mass explains difference in biomass partitioning between woody plant functional types

### 2014-10-15 manuscript/draftpaper.Rnw
Changed font to more readable opensans
Removed two counts tables as they were identical

\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\bibliographystyle{plain}

@@

\item We used a generalized additive model (GAM) to visualize the relationships.

\item We used linear mixed-effects models (with species within study as the random effect) to test for significance and to calculate confidence intervals for PFT-specific averages. Least-square means for LMF and LAR were calculated with the lsmeans package.

\item Variance partitioning with marginal (fixed effects) and conditional (fixed and random effects) R2 for linear mixed-effects models as reported by \cite{nakagawa_general_2013}.

@@

<<results='asis'>>=
printit(tab_mlfastba, caption="Number of observations used in the analysis of Mf/As. Individual plants (number of species).")
@

<<results='asis'>>=
printit(tab_alfastba, caption="Number of observations used in the analysis of Af/As. Individual plants (number of species).")
@

<<results='asis'>>=
printit(tab_lmf, caption="Number of observations used in the analysis of leaf mass fraction (LMF). Individual plants (number of species).")
@

<<results='asis'>>=
printit(tab_lar, caption="Number of observations used in the analysis of leaf area ratio (LAR). Individual plants (number of species).")
@

>>>>

\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage[default,osfigures,scale=0.95]{opensans}
\graphicspath{ {./figures/} }
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\bibliographystyle{plain}

@@

\item We used a generalized additive model (GAM) to visualize the relationships, but these were not used for formal inference.

\item We used linear mixed-effects models (with species within study as the random effect) to test for significance and to calculate confidence intervals for PFT-specific averages. Least-square means for LMF and LAR were calculated with the 'lsmeans' package.

\item All variables were log-transformed prior to analysis, to stabilize variance.

\item Variance partitioning with marginal (fixed effects) and conditional (fixed and random effects) $R^2$ for linear mixed-effects models as reported by \cite{nakagawa_general_2013}.

@@

<<results='asis'>>=
printit(tab_mlfastba, caption="Number of observations used in the analysis of $M_F/A_S$ and $A_F/A_S$. Individual plants (number of species). DA = Deciduous Angiosperm, EA = Evergreen Angiosperm, EG = Evergreen Gymnosperm.")
@

% <<results='asis'>>=
% printit(tab_alfastba, caption="Number of observations used in the analysis of Af/As. Individual plants (number of species). DA = Deciduous Angiosperm, EA = Evergreen Angiosperm, EG = Evergreen Gymnosperm.")
% @
%

<<results='asis'>>=
printit(tab_lmf, caption="Number of observations used in the analysis of leaf mass fraction (LMF) and leaf area ratio (LAR). Individual plants (number of species). DA = Deciduous Angiosperm, EA = Evergreen Angiosperm, EG = Evergreen Gymnosperm.")
@

% 
% <<results='asis'>>=
% printit(tab_lar, caption="Number of observations used in the analysis of leaf area ratio (LAR). Individual plants (number of species). DA = Deciduous Angiosperm, EA = Evergreen Angiosperm, EG = Evergreen Gymnosperm.")
% @
